Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-17 report/report.tex
Add Vanegas reference
Introduction to virtual cities by Vanegas

Description of the field of city reproduction \textbf{(Parish and Müller, 2001)}.

Picture of a virtual city.

Description of a virtual city and its contents.
Consisting of road network, buildings, details.
Roads have different types.

@@

Description of procedural modelling of cities
Importing geodata from online databases and converting it to a 3D city representation.
It would be labour intensive to recreate these .
Procedural models for city reproduction instead rely on programmatic solutions for converting map data to 3D road and building models, and composing them to a 3D world that the designer may continue to fine-tweak.
\textbf{(Müller et al, 2006)}

@@

% Writing:
% TODO: Write introduction section
    % TODO: read Vanega
% TODO: Write Collision study implementation section
    % TODO: Edge distance algorithm, algorithm

@@

>>>>

Cities consist of complex collections of buildings, blocks, parcels and neighbourhoods which are all interconnected via a street network, where individual streets can serve different types of traffic.
Virtual city reproduction has a growing number of applications, including visualization, urban planning and entertainment in the form of video games and 3D animation.
Traditionally, modelling virtual cities is a labour-intensive and time-consuming task.
In recent years there has been major research work into the field of procedural content generation, meaning automatic or semi automatic generation of 3D models
Such methods can indeed be used in the field of virtual city reproduction to reduce the labour required to reproduce accurate 3D representations of cities.
But the field of virtual city reproduction comes with its own host of challenges.
Urban environments are typically dense and large, spanning a few to hundreds of square kilometers, and are influenced by variables that are hard to quantify, including land policies, government plans, population changes and transportation infrastructure.
\textbf{(Vanegas et al, 2010)}.

@@

Description of procedural modelling of cities
Importing geodata from online databases and converting it to a 3D city representation.
It would be labour intensive to recreate these .
Procedural models for city reproduction instead rely on programmatic solutions for converting map data to 3D road and building models, and composing them to a 3D world that the designer may continue to fine-tweak through interfaces fo interactive editing.
\textbf{(Müller et al, 2006)}

@@

% Writing:
% TODO: Write introduction section
% TODO: Write Collision study implementation section
    % TODO: Edge distance algorithm, algorithm

@@

\bibitem{vanegas-10}
%TODO
Vanegas, C.
2010
Modelling the Appearance and Behaviour of Urban Spaces
